### 2011-05-12 paper.tex
fixed small thing about extensions

We can use this remarkable fact to finish the proof of Lemma \ref{amplifymainlemma}, thus proving Theorem \ref{amplify}.
\begin{proof}[Proof of Lemma \ref{amplifymainlemma} (iv)]
Take any function $f \in \parity \cdot C$. If $C$ is $\{\Sigma, \Pi, \parity\}$-constructible, we can assume that $f$ is defined everywhere; any function not defined everywhere can be extended to a function which is, simply by extending the innermost $\p$ function (see Remark \ref{equivtoold}).

We want to show that $\majority(f)$ is in $\parity \cdot C$. It is easy to see that $\majority(f) \in \p^{\parity \cdot C}$. For a given $k$-tuple $(x_1,x_2,...,x_k)$, we use the oracle call to $\parity \cdot C$ to determine how many of the $x_i$ are accepted in $L$, and how many are rejected. If at least half are accepted, we accept, and if more than half are rejected, we reject.

Thus, $\majority(f) \in \p^{\parity \cdot C}$. Thus, we can apply Theorem \ref{oracleparityc} to get that $\majority(f) \in \parity \cdot C$. Therefore $\parity \cdot C$ is closed under majority reductions.
\end{proof}

>>>>

We can use this remarkable fact to finish the proof of Lemma \ref{amplifymainlemma}, thus proving Theorem \ref{amplify}.
\begin{proof}[Proof of Lemma \ref{amplifymainlemma} (iv)]
Take any function $f \in \parity \cdot C$. If $C$ is $\{\Sigma, \Pi, \parity\}$-constructible, we can extend $f$ to some $\overline{f}$ which is defined everywhere; i.e. $\overline{f}(x) \ne \x$ for all $x$. To extend $f$ in this way, we simply extend the innermost $\p$ function (see Remark \ref{equivtoold}).

Now, we will show that $\majority(\overline{f})$ is in $\parity \cdot C$. It is easy to see that $\majority(\overline{f}) \in \p^{\parity \cdot C}$. For a given $k$-tuple $(x_1,x_2,...,x_k)$, we use the oracle call to $\parity \cdot C$ to determine how many of the $x_i$ are such that $\overline{f}(x) = 1$ and how many are such that $\overline{f}(x) = 0$. If at least half are accepted, we accept, and if more than half are rejected, we reject.

Thus, $\majority(\overline{f}) \in \p^{\parity \cdot C}$. Thus, we can apply Theorem \ref{oracleparityc} to get that $\majority(\overline{f}) \in \parity \cdot C$. But $\majority(\overline{f})$ is just an extension of $\majority(f)$, so $\majority(f) \in \parity \cdot C$. Therefore $\parity \cdot C$ is closed under majority reductions.
\end{proof}
